Type Error Telemetry at Scale

### 2023-09-29 programming23/paper.tex
threat: sessions vs people

\FILL{} cannot match sessions to codebases

@@

First of all, sampling is necessarily incomplete.
Though the data includes many thousands of sessions, it
may have missed a few critical sessions where a creator
adopted \mstrict{} mode, encountered \code{CodeTooComplex} errors,
and gave up.
Furthemore, our method of sampling by keystroke and by module switch
skews the data toward creators who, for whatever reason, do more
of these actions.
We have no access to other events (e.g., run locally, publish) due to privacy
concerns; future studies may wish to avoid this limitation by actively
recruiting subjects.

@@

Third, the total counts of type errors include a large number of syntax errors,
which have little to do with the Luau type system and are presumably easy for
creators to fix.
It would be better for the analysis to ignore these errors.
Indeed, our comparison between \FS{} errors in \mnocheck{} vs.
\mstrict{} mode~(\cref{f:error-changes}) might tell a very different story
without all the noise that syntax errors introduce.\todo{Why didn't
  YOU just filter them, then?!?}

Fourth, type analysis reports several errors at once and we have no idea which
errors, if any, creators intended to fix with their edits.
Thus, fixes may be a side effect of other plans, as seen in prior work~\cite{mfk-sigcse-2011}.
% This is the [DIFF] code from Marceau SIGCSE 2011.

>>>>

@@

First of all, sampling is necessarily incomplete.
Though the data includes many thousands of sessions, it
may have missed a few critical sessions where a creator
adopted \mstrict{} mode, encountered \code{CodeTooComplex} errors,
and gave up.
Furthemore, our method of sampling by keystroke and by module switch
skews the data toward creators who, for whatever reason, do more
of these actions.
We have no access to other events, e.g., run locally~(\cref{s:tel-limitations});
future studies may wish to avoid this limitation by actively
recruiting subjects.

@@

Third, session-based data has limitations.
A creator who closes and reopens Roblox Studio every day has
a much higher chance of generating telemetry than one who
leaves Studio open all week.
We have no way to reliably check whether multiple sessions are
reporting on the same codebase.
Sessions may end abruptly, for instance because of machine reboot,
instead of ending when the creator was finished editing code.

Fourth, the total counts of type errors include a large number of syntax errors,
which have little to do with the Luau type system and are presumably easy for
creators to fix.
It would be better for the analysis to ignore these errors.
Indeed, our comparison between \FS{} errors in \mnocheck{} vs.
\mstrict{} mode~(\cref{f:error-changes}) might tell a very different story
without all the noise that syntax errors introduce.\todo{Why didn't
  YOU just filter them, then?!?}

Fifth, type analysis reports several errors at once and we have no idea which
errors, if any, creators intended to fix with their edits.
Thus, fixes may be a side effect of other plans, as seen in prior work~\cite{mfk-sigcse-2011}.
% This is the [DIFF] code from Marceau SIGCSE 2011.
